### 2015-05-18 Manuscript/Missing_mammals-draft.tex
Citation style change

\documentclass[12pt,letterpaper]{article}

@@

\section{Introduction}
%We need fossils - dangerously paraphrased from the missing data paper
Studying both living and fossil taxa together in essential to fully understand macrovelutionary patterns and processes and is becoming increasingly common among evolutionary biologists \cite{jacksonwhat2006,quentaldiversity2010,dietlconservation2011,slaterunifying2013,fritzdiversity2013,Wood01032013}. Combining the global biodiversity by including both living and fossil in such studies allows, for example, to improve accuracy of the timing of diversification events (e.g. \cite{ronquista2012}), to better understand relationships among lineages (e.g. \cite{beckancient2014}) or to infer biogeographical patterns through time (e.g. \cite{Meseguer01032015}). %And add STD paper? Or that's too much self cites?
%We can use TEM for that
In order to perform such analysis, one must efficiently combine living and fossil taxa data in macroevolutionary models. One trending method, called the Total Evidence method \cite{eernissetaxonomic1993,ronquista2012}, allows to combine molecular data from living taxa and morphological data from both living and fossil taxa in a supermatrix (e.g. \cite{pyrondivergence2011,ronquista2012,schragocombining2013,slaterunifying2013,beckancient2014,Meseguer01032015}). This method not only allows to use all the available data but also allows to treat fossil taxa as tips rather than nodes \textit{via} integrative phylogenetic inference methods such as tip-dating \cite{ronquista2012,Drummond01082012,Wood01032013,BEASTmaster}.

%But missing data in living taxa problem
However, the Total Evidence method requires, by definition, a lot of data. One must collect both molecular data for living taxa as well as morphological data for both living and fossil taxa, two types of data that require fairly different technical skills (e.g. \cite{meredithimpacts2011} \textit{vs.} \cite{O'Leary08022013}). Additionally, entire sections of this data can sometimes be difficult or impossible to collect for every taxa present in the analysis. For example, fossil have really rarely molecular data available and morphological characters are rarely collected for living taxa when molecular data is available (e.g. \cite{slaterphylogenetic2013,beckancient2014}). This difference between both data can lead to topological errors in phylogenetic inference \cite{GuillermeCooper}. In fact, the ability of the Total Evidence method to recover correct topology is expected to decrease when there is a low overlap between morphological data from the living and the fossil taxa \cite{GuillermeCooper}. The effect of missing data is most important on topology when too few living taxa have available morphological data \cite{GuillermeCooper}. For example, if there is no morphological available for any living taxa within an entire clade, it is impossible to link a fossil taxon to this clade because no morphological data will overlap between the fossil (regardless the amount of data available for the fossil) and the living taxa (that have no morphological data). This property of the Total Evidence method can rapidly lead to important topological incongruities because the fossil will only be able to branch to a clade of living taxa that contains morphological data, even if in reality, the fossil taxon does not belong to that clade \cite{GuillermeCooper} (see figure ~\ref{Figure_missing_data_problem}).

@@

%What we're doing
It is therefore crucial to understand the distribution of the available morphological data for living taxa in a clade before using a Total Evidence approach because missing living taxa with morphological data can lead to two topological artefacts: (1) the impossibility for a fossil to branch in the right clade if there is no morphological data available in this clade \cite{GuillermeCooper}; and (2) the higher probability for a fossil to branch within a wrong clade that has more morphological data available for living taxa than the right clade \cite{GuillermeCooper}. In this study, we assess the level of available morphological data in living mammals in order to highlight the two caveats described above.
%In this study we investigate the amount of living mammal taxa with available morphological data to detect the two potential caveats described above that could lead to topological errors when building Total Evidence mammal phylogenetic trees.
We collected living mammals morphological data from @256 phylogenetic matrices available online and measured the proportion of morphological data availability for each mammalian order. Additionally, in the mammalian orders where data was missing, we estimated the structure of the available data to detect if the available data was biased towards certain clades only or if it was randomly distributed using the Net Relatedness Index \cite{webb2002phylogenies}.

@@

\section{Material and Methods}
\subsection{Matrices search}
To investigate the available living taxa with morphological data, we downloaded morphological matrices from three main public databases: morphobank (\texttt{http://www.morphobank.org/}) \cite{morphobank}, Graeme Lloyd's website (\texttt{http://graemetlloyd.com/}) and Ross Mounce's GitHub repository (\texttt{https://github.com/rossmounce}). We downloaded all the matrices containing any fossil or living mammal taxa from these databases. Additionally we ran a thorough Google Scholar search for matrices that might not have been uploaded on the previously cited data bases. We downloaded the additional morphological characters matrices from the 20 first Google search results matching with our selected keywords and with any of the 35 taxonomic levels (see supplementary materials for detailed description of the procedure). We downloaded 256 % @@@ Number of matrices
matrices containing a total of 9411 % @@@ Number of living OTUs
operational taxonomic units (OTUs) from the combination of both searches (public repositories and Google Scholar). The list of matrices is available in the supplementary materials.

We then transformed all the matrices to be in the same nexus format. We also standardised the taxonomic nomenclature by fixing invalid binomial inputs to match with the official taxonomic nomenclature rules (i.e. \textit{H. sapiens} was transformed in \textit{Homo sapiens}). We assigned each species as being either living or fossil using a taxonomic matching algorithm. We designated as living OTU all the OTUs that where either present in \cite{FritzTree} or \cite{wilson2005mammal}. We designated as fossil OTUs all the OTUs that where present in the Paleobiology database. For the OTUs neither labelled as living or fossil we tried to decompose the OTUs name (i.e. \textit{Homo$\_$sapiens} became \textit{Homo} and \textit{sapiens}) and tried to match the first element with any taxonomic level (Family, Genus, Species, etc.) from \cite{wilson2005mammal}. The matching OTUs where labelled as living and the ones still not matching where ignored and labelled as non-applicable (NA; see supplementary material for more details on the taxonomic matching algorithm).

\subsection{Data availability analysis}
\subsubsection{Number of characters threshold}
From all the 256 % @@@ Number of matrices
matrices, we selected only the ones that displayed at least 100 morphological characters per OTU. This arbitrary threshold of a minimal number of morphological characters was chosen to be in adequacy with \cite{GuillermeCooper} and \cite{harrisonamong-character2014}. Also this threshold avoids biases towards small matrices that could be either not informative \cite{wagner2000} (e.g. too few characters not allowing character overlap among matrices) or made of non-applicable characters \cite{Brazeau2011} (e.g. antlers which are sexual dimorphic characters proper to a specific clade).

\subsubsection{Data availability}
To assess the data availability per mammal order, we calculated the percentage of OTUs with morphological data for three different taxonomic levels: Family, Genus and Species. We highlighted all the orders containing less than 25\% of living taxa with morphological data because their amount of missing data ($>$75\%) was higher than in \cite{GuillermeCooper} and therefore highly probable of having wrong topology due to the missing data. On the opposite, orders with up to 25\% of missing data (75\% of available data) were shown to have no significant effect on topology \cite{GuillermeCooper}. We therefore used this value as a threshold of "good" data sampling.

\subsubsection{Available data structure}
For the orders with no morphological data for all its OTUs at the three different taxonomic levels (Family, Genus and Species), we investigated the structure of the available data to test if it was either (i) randomly distributed, (ii) over-dispersed or (iii) clustered. To measure the structure of the available data we used classic community structure metric from the \texttt{picante} R package \cite{picante}. We compared the structure of the available data for each order to the structure of a potentially fully sampled order (i.e. only the OTUs with available morphological data \textit{versus} all the OTUs).
For each orders and taxonomic levels that presented OTUs with no available morphological data, we calculated the Net Relatedness Index (NRI) which quantifies the overall distribution of the data with negative values showing more dispersed data and positive values more clustered data than expected by the null model (random) \cite{webb2002phylogenies}. We choose to present only the NRI values because they have been shown to be slightly less sensitive to the structure of the phylogeny (i.e. branch length and topology) \cite{NRI,journal.pone.0004390} but we also calculated the two other common phylogenetic structure indices: Faith's Phylogenetic Distance (PD) \cite{Faith19921} and the Nearest Taxon Index (NTI) \cite{webb2002phylogenies}. Both metrics are available in the Supplementary results.

@@

\subsection{Data availability}
We extracted 1422 living mammal OTUs from the 256 matrices with a minimum of 6 characters and a maximum of 4541 per OTU. After removing all the matrices with less than 100 morphological characters, the number of extracted living mammals OTUs was down to 815. 11/28 orders have less than 25\% of taxa with morphological data at a species level and 24/28 orders have less than 75\% taxa with available morphological data. At the Genus level however only 3/28 orders have less than 25\% of taxa with morphological data and 16/28 have less than 75\%. Finally, at the family level no order has less than 25\% taxa with available morphological data and only 5/28 have less than 75\% (table \ref{Table_morpho_taxa_proportion}).

@@

\subsection{Available data structure}
Among the orders containing at least one OTU with no available morphological data, only two orders are significantly clustered: Carnivora and Chiroptera both at the species and the genus level (table~\ref{Table_data_structure}).

@@

Two contrasted results are shown on figures \ref{Figure_example_coverageA} and \ref{Figure_example_coverageB} with randomly distributed data in Cetartiodactyla (figure \ref{Figure_example_coverageA}) and clustered available data in Carnivora (mainly Canidae; figure \ref{Figure_example_coverageB}).

@@

\section{Discussion}
Our results show that even though relations among living mammals are well known in a molecular framework (e.g. \cite{FritzTree,meredithimpacts2011,May-Collado-PeerJ}) only little morphological data is available. This is primarily due to the fact that that morphological studies are mainly focusing on fossil taxa rather than living taxa (e.g. \cite{O'Leary08022013,ni2013oldest}). However, data availability varies in its structure as well as across taxonomic levels. Higher taxonomic levels are always better sampled than lower ones (table \ref{Table_morpho_taxa_proportion}) and within these taxonomic levels, the structure of available data is mostly random apart for two orders (table \ref{Table_data_structure}).

%\subsection{Data availability}
The amount of living taxa with no available morphological data was surprisingly high at the species level: 24/28 orders have less than 75\% taxa with available morphological data (and two of the 28 orders are monospecific). This threshold of 75\% available data is the maximum amount of possible missing data (25\%) before having a significant effect on the topology of Total Evidence trees \cite{GuillermeCooper}. Beyond this threshold, there is a noteworthy displacement of the wildcard taxa (\textit{sensu} \cite{kearneyfragmentary2002}) as well as a important decrease in the conservation of clades \cite{GuillermeCooper}. At the species level within most orders of mammals, it is therefore likely to see topological artefacts for the placement of fossil taxa. However, the data availability seems to be less an issue at higher taxonomic level (i.e. the Genus and the Family level). This point is important to consider from a practical point of view because of the slight discrepancy between neontological and palaeontological species. While neontological species are described on accurately measured morphology, genetic distance, spacial distribution and even behaviour (e.g. \cite{kellymolecular2014}); palaeontological data can be based only on morphological, spatial and temporal data (e.g. \cite{ni2013oldest}). Because of this difference between neontological species (\textit{sensu} reproductive isolates) and paleontological species (\textit{sensu} morpho-species), most palaeontological studies are using the Genus level for their smallest taxonomic OTU (e.g. \cite{ni2013oldest,O'Leary08022013}). In this frame of palaeontological data usage, the data availability at the Genus level in living mammals should be our priority concern.

%\subsection{Available data structure}
Regardless the low level of available data, it is encouraging that for most orders (except Carnivora and Chiroptera), it is randomly distributed across the phylogeny. Therefore, it is likely that the addition of fossil taxa within these orders will not be biased by oversampling but will probably branch near the taxa that has the most similar available data (as expected). When only few data is available, the ideal scenario will be that the data is over-dispersed (i.e. that there is data in at least every sub-clade) in order to maximize the possibilities of the fossil to branch in the right clade. In the second scenario, when the data is randomly distributed we expected no special bias in the placement of the fossil \cite{GuillermeCooper}. However, in the third scenario, when the data is clustered we expect two major biases to occur: (1) first, the fossil will not be able to branch within a clade containing no data (e.g. Herpestidae in Carnivora; figure \ref{Figure_missing_data_problem} and \ref{Figure_example_coverageB}), and (2) second, the fossil will have a higher probability, at random, to branch within the clade containing most of the available data (e.g. a Carnivora fossil will have more chance to branch, randomly, to the Canidae clade than any other clade in Carnivora; figure \ref{Figure_example_coverageB}).

%For example in Carnivora, their is no available data for Herpestidae, therefore any fossil Herpestidae will not be able to be correctly placed in the phylogeny (figure ~\ref{Figure_example_coverageB}). On the other hand, any Carnivora fossil with uncertain phylogenetic affinities (\textit{Incertae sedis}) will have a higher probability of branching by chance within the Canidae because they are oversampled within the Carnivora (figure ~\ref{Figure_example_coverageB}).

%Caveats
In this study, we treated all morphological matrices to be equal in a similar way that molecular matrices are: for example if a matrix A contains 100 characters for taxa X and Y, and a matrix B contains 50 characters for taxa X and Z, we assumed that both matrices can be combined in a supermatrix way leading to a matrix containing 150 characters for taxon X, 100 for taxon Y and 50 for taxon Z. However, it is clear that morphological data cannot be treated that way \cite{Brazeau2011}. In fact, for the same taxon, some characters might overlap (e.g. matrix A has a character coding for the shape of a particular morphological feature and matrix B as a first character coding for the presence of this morphological feature and a second one coding for its shape; in this case, these three characters are compound characters \cite{Brazeau2011}). However, in reasonably sized matrices ($>$ 100 characters \cite{GuillermeCooper,harrisonamong-character2014}) it is more likely that a number of characters are consistently conserved among the different matrices (e.g. \cite{ross1998phylogenetic,seiffert2003fossil,marivaux2005anthropoid,seiffert2005basal,bloch2007new,kay2008anatomy,silcox2008biogeographic,seiffert2009convergent,tabuce2009anthropoid,boyer2010astragalar,seiffert2010fossil,marivaux2013djebelemur,ni2013oldest}). A conservative approach to avoid compound characters could be to select only the latest matrix for each taxon.

%Let's code some data
Following the recommendations in \cite{GuillermeCooper}, one should code morphological characters for a maximum of living species in order to improve the topology of Total Evidence trees containing both living and fossil taxa. Since the data for living mammals is usually easily available in world wide vast natural history collections, we propose that an increased effort in coding morphological characters from living species should be done via engaging in collaborative data collection projects through web portals such as \textit{morphobank} \cite{morphobank}.

@@

\bibliographystyle{vancouver}
\bibliography{References}

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{natbib}

@@

\section{Introduction}
%We need fossils - dangerously paraphrased from the missing data paper
Studying both living and fossil taxa together in essential to fully understand macrovelutionary patterns and processes and is becoming increasingly common among evolutionary biologists \citep{jacksonwhat2006,quentaldiversity2010,dietlconservation2011,slaterunifying2013,fritzdiversity2013,Wood01032013}. Combining the global biodiversity by including both living and fossil in such studies allows, for example, to improve accuracy of the timing of diversification events \citep[e.g.][]{ronquista2012}, to better understand relationships among lineages \citep[e.g.][]{beckancient2014} or to infer biogeographical patterns through time \citep[e.g.][]{Meseguer01032015}. %And add STD paper? Or that's too much self cites?
%We can use TEM for that
In order to perform such analysis, one must efficiently combine living and fossil taxa data in macroevolutionary models. One trending method, called the Total Evidence method \citep{eernissetaxonomic1993,ronquista2012}, allows to combine molecular data from living taxa and morphological data from both living and fossil taxa in a supermatrix \citep[e.g.][]{pyrondivergence2011,ronquista2012,schragocombining2013,slaterunifying2013,beckancient2014,Meseguer01032015}. This method not only allows to use all the available data but also allows to treat fossil taxa as tips rather than nodes \textit{via} integrative phylogenetic inference methods such as tip-dating \citep{ronquista2012,Drummond01082012,Wood01032013,BEASTmaster}.

%But missing data in living taxa problem
However, the Total Evidence method requires, by definition, a lot of data. One must collect both molecular data for living taxa as well as morphological data for both living and fossil taxa, two types of data that require fairly different technical skills \citep[e.g.][]{meredithimpacts2011} \textit{vs.} \citep{O'Leary08022013}. Additionally, entire sections of this data can sometimes be difficult or impossible to collect for every taxa present in the analysis. For example, fossil have really rarely molecular data available and morphological characters are rarely collected for living taxa when molecular data is available \citep[e.g.][]{slaterphylogenetic2013,beckancient2014}. This difference between both data can lead to topological errors in phylogenetic inference \citep{GuillermeCooper}. In fact, the ability of the Total Evidence method to recover correct topology is expected to decrease when there is a low overlap between morphological data from the living and the fossil taxa \citep{GuillermeCooper}. The effect of missing data is most important on topology when too few living taxa have available morphological data \citep{GuillermeCooper}. For example, if there is no morphological available for any living taxa within an entire clade, it is impossible to link a fossil taxon to this clade because no morphological data will overlap between the fossil (regardless the amount of data available for the fossil) and the living taxa (that have no morphological data). This property of the Total Evidence method can rapidly lead to important topological incongruities because the fossil will only be able to branch to a clade of living taxa that contains morphological data, even if in reality, the fossil taxon does not belong to that clade \citep{GuillermeCooper} (see figure ~\ref{Figure_missing_data_problem}.

@@

%What we're doing
It is therefore crucial to understand the distribution of the available morphological data for living taxa in a clade before using a Total Evidence approach because missing living taxa with morphological data can lead to two topological artefacts: (1) the impossibility for a fossil to branch in the right clade if there is no morphological data available in this clade \citep{GuillermeCooper}; and (2) the higher probability for a fossil to branch within a wrong clade that has more morphological data available for living taxa than the right clade \citep{GuillermeCooper}. In this study, we assess the level of available morphological data in living mammals in order to highlight the two caveats described above.
%In this study we investigate the amount of living mammal taxa with available morphological data to detect the two potential caveats described above that could lead to topological errors when building Total Evidence mammal phylogenetic trees.
We collected living mammals morphological data from @256 phylogenetic matrices available online and measured the proportion of morphological data availability for each mammalian order. Additionally, in the mammalian orders where data was missing, we estimated the structure of the available data to detect if the available data was biased towards certain clades only or if it was randomly distributed using the Net Relatedness Index \citep{webb2002phylogenies}.

@@

\section{Material and Methods}
\subsection{Matrices search}
To investigate the available living taxa with morphological data, we downloaded morphological matrices from three main public databases: morphobank (\texttt{http://www.morphobank.org/} \citep{morphobank}, Graeme Lloyd's website (\texttt{http://graemetlloyd.com/} and Ross Mounce's GitHub repository (\texttt{https://github.com/rossmounce}. We downloaded all the matrices containing any fossil or living mammal taxa from these databases. Additionally we ran a thorough Google Scholar search for matrices that might not have been uploaded on the previously cited data bases. We downloaded the additional morphological characters matrices from the 20 first Google search results matching with our selected keywords and with any of the 35 taxonomic levels (see supplementary materials for detailed description of the procedure). We downloaded 256 % @@@ Number of matrices
matrices containing a total of 9411 % @@@ Number of living OTUs
operational taxonomic units (OTUs) from the combination of both searches (public repositories and Google Scholar). The list of matrices is available in the supplementary materials.

We then transformed all the matrices to be in the same nexus format. We also standardised the taxonomic nomenclature by fixing invalid binomial inputs to match with the official taxonomic nomenclature rules (i.e. \textit{H. sapiens} was transformed in \textit{Homo sapiens}. We assigned each species as being either living or fossil using a taxonomic matching algorithm. We designated as living OTU all the OTUs that where either present in \citep{FritzTree} or \citep{wilson2005mammal}. We designated as fossil OTUs all the OTUs that where present in the Paleobiology database. For the OTUs neither labelled as living or fossil we tried to decompose the OTUs name (i.e. \textit{Homo$\_$sapiens} became \textit{Homo} and \textit{sapiens} and tried to match the first element with any taxonomic level (Family, Genus, Species, etc.) from \citep{wilson2005mammal}. The matching OTUs where labelled as living and the ones still not matching where ignored and labelled as non-applicable (NA; see supplementary material for more details on the taxonomic matching algorithm).

\subsection{Data availability analysis}
\subsubsection{Number of characters threshold}
From all the 256 % @@@ Number of matrices
matrices, we selected only the ones that displayed at least 100 morphological characters per OTU. This arbitrary threshold of a minimal number of morphological characters was chosen to be in adequacy with \citep{GuillermeCooper} and \citep{harrisonamong-character2014}. Also this threshold avoids biases towards small matrices that could be either not informative \citep{wagner2000} (e.g. too few characters not allowing character overlap among matrices) or made of non-applicable characters \citep{Brazeau2011} (e.g. antlers which are sexual dimorphic characters proper to a specific clade).

\subsubsection{Data availability}
To assess the data availability per mammal order, we calculated the percentage of OTUs with morphological data for three different taxonomic levels: Family, Genus and Species. We highlighted all the orders containing less than 25\% of living taxa with morphological data because their amount of missing data ($>$75\%) was higher than in \citep{GuillermeCooper} and therefore highly probable of having wrong topology due to the missing data. On the opposite, orders with up to 25\% of missing data (75\% of available data) were shown to have no significant effect on topology \citep{GuillermeCooper}. We therefore used this value as a threshold of "good" data sampling.

\subsubsection{Available data structure}
For the orders with no morphological data for all its OTUs at the three different taxonomic levels (Family, Genus and Species), we investigated the structure of the available data to test if it was either (i) randomly distributed, (ii) over-dispersed or (iii) clustered. To measure the structure of the available data we used classic community structure metric from the \texttt{picante} R package \citep{picante}. We compared the structure of the available data for each order to the structure of a potentially fully sampled order (i.e. only the OTUs with available morphological data \textit{versus} all the OTUs).
For each orders and taxonomic levels that presented OTUs with no available morphological data, we calculated the Net Relatedness Index (NRI) which quantifies the overall distribution of the data with negative values showing more dispersed data and positive values more clustered data than expected by the null model (random) \citep{webb2002phylogenies}. We choose to present only the NRI values because they have been shown to be slightly less sensitive to the structure of the phylogeny (i.e. branch length and topology) \citep{NRI,journal.pone.0004390} but we also calculated the two other common phylogenetic structure indices: Faith's Phylogenetic Distance (PD) \citep{Faith19921} and the Nearest Taxon Index (NTI) \citep{webb2002phylogenies}. Both metrics are available in the Supplementary results.

@@

\subsection{Data availability}
We extracted 1422 living mammal OTUs from the 256 matrices with a minimum of 6 characters and a maximum of 4541 per OTU. After removing all the matrices with less than 100 morphological characters, the number of extracted living mammals OTUs was down to 815. 11/28 orders have less than 25\% of taxa with morphological data at a species level and 24/28 orders have less than 75\% taxa with available morphological data. At the Genus level however only 3/28 orders have less than 25\% of taxa with morphological data and 16/28 have less than 75\%. Finally, at the family level no order has less than 25\% taxa with available morphological data and only 5/28 have less than 75\% (table \ref{Table_morpho_taxa_proportion}.

@@

\subsection{Available data structure}
Among the orders containing at least one OTU with no available morphological data, only two orders are significantly clustered: Carnivora and Chiroptera both at the species and the genus level (table~\ref{Table_data_structure}.

@@

Two contrasted results are shown on figures \ref{Figure_example_coverageA} and \ref{Figure_example_coverageB} with randomly distributed data in Cetartiodactyla (figure \ref{Figure_example_coverageA} and clustered available data in Carnivora (mainly Canidae; figure \ref{Figure_example_coverageB}.

@@

\section{Discussion}
Our results show that even though relations among living mammals are well known in a molecular framework \citep[e.g.][]{FritzTree,meredithimpacts2011,May-Collado-PeerJ} only little morphological data is available. This is primarily due to the fact that that morphological studies are mainly focusing on fossil taxa rather than living taxa \citep[e.g.][]{O'Leary08022013,ni2013oldest}. However, data availability varies in its structure as well as across taxonomic levels. Higher taxonomic levels are always better sampled than lower ones (table \ref{Table_morpho_taxa_proportion} and within these taxonomic levels, the structure of available data is mostly random apart for two orders (table \ref{Table_data_structure}.

%\subsection{Data availability}
The amount of living taxa with no available morphological data was surprisingly high at the species level: 24/28 orders have less than 75\% taxa with available morphological data (and two of the 28 orders are monospecific). This threshold of 75\% available data is the maximum amount of possible missing data (25\%) before having a significant effect on the topology of Total Evidence trees \citep{GuillermeCooper}. Beyond this threshold, there is a noteworthy displacement of the wildcard taxa (\textit{sensu} \citep{kearneyfragmentary2002} as well as a important decrease in the conservation of clades \citep{GuillermeCooper}. At the species level within most orders of mammals, it is therefore likely to see topological artefacts for the placement of fossil taxa. However, the data availability seems to be less an issue at higher taxonomic level (i.e. the Genus and the Family level). This point is important to consider from a practical point of view because of the slight discrepancy between neontological and palaeontological species. While neontological species are described on accurately measured morphology, genetic distance, spacial distribution and even behaviour \citep[e.g.][]{kellymolecular2014}; palaeontological data can be based only on morphological, spatial and temporal data \citep[e.g.][]{ni2013oldest}. Because of this difference between neontological species (\textit{sensu} reproductive isolates) and paleontological species (\textit{sensu} morpho-species), most palaeontological studies are using the Genus level for their smallest taxonomic OTU \citep[e.g.][]{ni2013oldest,O'Leary08022013}. In this frame of palaeontological data usage, the data availability at the Genus level in living mammals should be our priority concern.

%\subsection{Available data structure}
Regardless the low level of available data, it is encouraging that for most orders (except Carnivora and Chiroptera), it is randomly distributed across the phylogeny. Therefore, it is likely that the addition of fossil taxa within these orders will not be biased by oversampling but will probably branch near the taxa that has the most similar available data (as expected). When only few data is available, the ideal scenario will be that the data is over-dispersed (i.e. that there is data in at least every sub-clade) in order to maximize the possibilities of the fossil to branch in the right clade. In the second scenario, when the data is randomly distributed we expected no special bias in the placement of the fossil \citep{GuillermeCooper}. However, in the third scenario, when the data is clustered we expect two major biases to occur: (1) first, the fossil will not be able to branch within a clade containing no data (e.g. Herpestidae in Carnivora; figure \ref{Figure_missing_data_problem} and \ref{Figure_example_coverageB}, and (2) second, the fossil will have a higher probability, at random, to branch within the clade containing most of the available data (e.g. a Carnivora fossil will have more chance to branch, randomly, to the Canidae clade than any other clade in Carnivora; figure \ref{Figure_example_coverageB}.

%For example in Carnivora, their is no available data for Herpestidae, therefore any fossil Herpestidae will not be able to be correctly placed in the phylogeny (figure ~\ref{Figure_example_coverageB}. On the other hand, any Carnivora fossil with uncertain phylogenetic affinities (\textit{Incertae sedis} will have a higher probability of branching by chance within the Canidae because they are oversampled within the Carnivora (figure ~\ref{Figure_example_coverageB}.

%Caveats
In this study, we treated all morphological matrices to be equal in a similar way that molecular matrices are: for example if a matrix A contains 100 characters for taxa X and Y, and a matrix B contains 50 characters for taxa X and Z, we assumed that both matrices can be combined in a supermatrix way leading to a matrix containing 150 characters for taxon X, 100 for taxon Y and 50 for taxon Z. However, it is clear that morphological data cannot be treated that way \citep{Brazeau2011}. In fact, for the same taxon, some characters might overlap (e.g. matrix A has a character coding for the shape of a particular morphological feature and matrix B as a first character coding for the presence of this morphological feature and a second one coding for its shape; in this case, these three characters are compound characters \citep{Brazeau2011}. However, in reasonably sized matrices ($>$ 100 characters \citep{GuillermeCooper,harrisonamong-character2014} it is more likely that a number of characters are consistently conserved among the different matrices \citep[e.g.][]{ross1998phylogenetic,seiffert2003fossil,marivaux2005anthropoid,seiffert2005basal,bloch2007new,kay2008anatomy,silcox2008biogeographic,seiffert2009convergent,tabuce2009anthropoid,boyer2010astragalar,seiffert2010fossil,marivaux2013djebelemur,ni2013oldest}. A conservative approach to avoid compound characters could be to select only the latest matrix for each taxon.

%Let's code some data
Following the recommendations in \citep{GuillermeCooper}, one should code morphological characters for a maximum of living species in order to improve the topology of Total Evidence trees containing both living and fossil taxa. Since the data for living mammals is usually easily available in world wide vast natural history collections, we propose that an increased effort in coding morphological characters from living species should be done via engaging in collaborative data collection projects through web portals such as \textit{morphobank} \citep{morphobank}.

@@

\bibliographystyle{sysbio}
\bibliography{References}
